---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Dollywood Attraction Directory Explorer

The `Dollywood` package allows users to explore the rides and attractions at [Dollywood Amusement Park] (https://www.dollywood.com/) in Pigeon Forge, Tennessee. Users of this package have the ability to search for and filter these attractions based on factors like their name, their location in the park, and more. 

In addition, users have the ability to pull an image of each attraction.

<!-- badges: start -->
[![R-CMD-check](https://github.com/abbyhunt24/sds270project/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/abbyhunt24/sds270project/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/abbyhunt24/sds270project/graph/badge.svg)](https://app.codecov.io/gh/abbyhunt24/sds270project)
<!-- badges: end -->

The `Dollywood` package provides an R interface to retrieve data about [Dollywood rides]("https://www.dollywood.com/themepark/rides/"). 

## Installation

You can install the development version of Dollywood from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("abbyhunt24/sds270project")
```

## Usage

This package allows users to filter the Dollywood attractions for a variety of characteristics. The following is an example of using the `dolly_search()` function to search for a ride by name.

In addition, the `ride_pic()` function allows users to generate an image of each ride.

```{r example}
library(dollywoodR)

barnstormer <- dolly_search(rides_df, "name", "Barnstormer")
str(barnstormer)

barnstormer_pic <- ride_pic(rides_df, "Barnstormer")
```

