---
title: "Using the DollyWood package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the DollyWood package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Browsing Dollywood Rides & Attractions

The main function of the dollywood package is to let you browse Dollywood rides and attractions from within R. Let's see how we can accomplish this. First, load the `dollywoodR` package.

```{r setup}
library(dollywoodR)
```


Then, use the `dolly_search()` function to retrieve information about a particular ride. We'll retrieve information about the ride "Barnstormer", so we'll set the name of the ride argument to "Barnstormer".

```{r}
Barnstormer_info <- dolly_search(rides_df, "name", "Barnstormer")
```


The `ride_pic()` function takes the list of metadata, and displays the actual image of the ride in the plot window:

```{r}
ride_pic(rides_df, "Barnstormer")
```







